% textidote: ignore begin
\section{Perspectivation}\label{sec:perspectivation}
% textidote: ignore end

% TODO write more here

Another solution to the problem is one made by the Danish company FynBus~\cite{fynbus2023}.
Their solutions have several similarities to our solution.
Most notably, as seen in~\ref{tab:similarities-between-ours-and-fynbus's-solution}, is the input parameters.
This is however to be expected, as these parameters are important for potential users.

\begin{table}[ht]
    \centering
    \begin{tabular}{|l|p{5cm}|p{5cm}|}
        \hline
        \textbf{Topics} & \textbf{Contents} \\
        \hline
        Parameters & Both programs has price, time and environment as input parameters \\
        \hline
        Output & Both programs provides information about the parameters based on route data \\
        \hline
    \end{tabular}
    \caption{Similarities between ours and Fynbus's solution.}
    \label{tab:similarities-between-ours-and-fynbus's-solution}
\end{table}

The differences are mentioned in~\ref{tab:differences-between-ours-and-fynbus's-solution} and includes insignificant as
well as significant differences.
An insignificant difference is the availability of the Fynbus solution, as theirs is an internet application most
likely written in the HTML programming language.
As we are required to write in the C programming language, it is not in scope to make a program solution that has a more
complicated UI than the terminal window.

\begin{table}[ht]
    \centering
    \begin{tabular}{|l|p{5cm}|p{5cm}|}
        \hline
        \textbf{Topics} & \textbf{Our solution} & \textbf{Fynbus's solution} \\
        \hline
        UI & Terminal window & Intuitive and interactive GUI \\
        \hline
        Availability & Has to be run locally as a .exe-file & Internet application \\
        \hline
        Frontend & Default terminal window & Beautiful simple design \\
        \hline
        Focus & Informational service as well as personal optimization for public transport routes & Informational service \\
        \hline
    \end{tabular}
    \caption{Differences between ours and Fynbus's solution.}
    \label{tab:differences-between-ours-and-fynbus's-solution}
\end{table}

A very significant difference however is that of the focus of the program.
As mentioned in~\ref{tab:differences-between-ours-and-fynbus's-solution} Fynbus's solutions main focus is to inform the
user of the consequences of different transport types in their routines.
This topic of focus is what makes our program vastly different to Fynbus's solution, as our program, as well as inform
the user the same way Fynbus's solutions does, also makes a prioritized list of the available public transport routes
and ranks them based on the users preferences.
