% textidote: ignore begin
\section{Extant solutions and their operational mechanisms}\label{sec:extant-solutions-and-their-operational-mechanisms}
% textidote: ignore end

Commuting is one of the staples, so to speak, of modern life, and a central part of the post-modern industrialized
society.
As cities rapidly grew after the industrial revolution and more and more large-scale workplaces became the norm in
cities, people started commuting to work from suburban areas to the city as mentioned earlier.

This question especially became relevant in recent times due to the increasingly noticeable effects of climate change
and the scientific evidence that increased \unit{CO_{2}} emissions greatly contribute to climate change.
Other questions the modern-day commuter might ask themselves are: Do I need/want to commute every day, or is it ok if I
work from home part of the week?
What should be the balance between cost and environmental protection?
Do I live in an area where the availability of public means of transportation is scarce, so I am more inclined to use a
car?
One of the simpler questions someone that considers commuting could ask themselves is merely: What commuting route
should I choose?
With the advent of the digital age and smartphones, the answer to this question have become commuting planner
applications, that have become increasingly popular in recent years, helping individuals plan their daily commutes
efficiently and minimize travel-related stress.
These applications offer various features and functionalities, but they often have shortcomings that prevent the
commuter from more advanced planning strategies, including the lack of easy access to cost and environmental impact
information, e.g., how much \unit{CO_{2}} will be spent on a trip, how much a trip will cost, as well as limited user
control over how these factors are weighed in route calculations.
Existing solutions include the (mostly) worldwide available Google Maps, the popular Danish Rejseplanen service and a
couple of other mobile and web applications that are not location-bound but can be used internationally, like
\url{https://commute.org/}.
We will now look at some existing solutions and discuss their shortcomings to better understand the root of the problem.

\input{problem-analysis/google-maps}
\input{problem-analysis/rejseplanen}
\input{problem-analysis/apple-maps}
