\section{Workflows and routines}\label{sec:workflows-and-routines}

In this section, we will discuss the development team's routines and workflows to gain a better understanding of how
the development process looked like.
The team's workflow for both the program and the report consisted of collaboration, communication, and version control.
Microsoft Teams was used for communication, Trello was used to assign tasks, and GitHub was used for the development of
the project.
Discussions were held in person and Microsoft Teams.
After the discussions, the team would create Trello cards for the task and assign them to individual members.
The GitHub repository has separate branch for each member of the team.
The team would work on their personal branch and then create a Pull Request with the purpose to merge the changes to the
main branch.
The Pull Request would then have to be reviewed by at least 2 other members before it could be merged.
After the merge, the person responsible for the changes will reset their branch and reuse it for the next task.
This workflow was used for both the program and the report.

GitHub has the added benefit of Actions, which is a CI/CD tool.
The team has set up different actions for the program and the report.
After a Commit on the program, GitHub will execute ClangTidy and ClangFormat workflows, that ensure that the code is
properly formatted and that there are no errors in the code.
The report has a workflow that will check for grammatical errors using TeXtidote and then compile the report into a PDF
file, which the team can then download and review.

The team had a weekly meeting with the supervisor, where the team would discuss the progress of the project.
Every meeting would start with a Code Review, where the team would go through the program and discuss the changes made
since the last meeting.
Occasionally, the team would also use the Scrum method to catch up on the progress of the project.
The team would discuss what they had done since the last meeting, what they were currently working on, and what they
would do next.
