%! Author = simon
%! Date = 04-11-2023

% Preamble
\documentclass[11pt]{article}
\title{Existing solutions}


% Packages
\usepackage{amsmath}

% Document
\begin{document}
    \maketitle
    \begin{abstract}
        In this section, we will discuss extant solutions and their operational mechanisms pertaining to the provided
        problem statement.
        We will analyze prominent software applications in the market,
        including Rejseplanen,Google Maps, and Apple Maps.
    \end{abstract}


    \section{Rejseplanen}\label{sec:rejseplanen}

    \textbf{What is Rejseplanen?}

    The ``Rejseplanen'' is an online service used in Denmark to plan journeys using public transport.
    It is used to find information about routes, timings, prices and ticket purchases for trains, buses, metro, trams and ferries
    throughout the country.\cite{Rejseplanen} \newline

    With ``Rejseplanen'', you can input your departure point and destination point to get information about the fastest,
    cheapest or most convenient way to travel from point A to B using public transport.
    The service provides detailed information about the departure times, transfers, expected arrival times and prices.
    It also provides any additional information about the delays or canceled departures in the operation of public transport.\cite{Rejseplanen}\newline

    \subsection{Data Sources for Rejseplanen}\label{subsec:where-does-rejseplanen-get-their-data-from?}

    Rejseplanen is jointly owned by DSB, Movia, Metroselskabet, NT, Midttrafik, Sydtrafik, Fynbus, and BAT.
    As a result of its ownership by these various transportation service providers, Rejseplanen has access to the
    data necessary to determine the most efficient public transport routes.

    \subsection{What makes Rejseplanen great?}\label{subsec:what-makes-rejseplanen-great?}
    \begin{description}
        \item [Comprehensive Data Integration] - Rejseplanen integrates data from various transportation providers, thus ensuring up-to-date and accurate information
        \item [Very efficient] - Rejseplanen provides a quick and convenient travel plan, saving time for daily commuters
        \item [User friendly] - Rejseplanen provides additional features such as filtering out specific trains or buses, so your route matches your personal preferences and enhancing the user experience
    \end{description}


    \section{Google Maps / Apple Maps}\label{sec:google-maps-/-apple-maps}

    \textbf{What is Google Maps}

    Google Maps is another online service used for travelling.
    It is one of the most extensive and detailed mapping databases globally.
    Its comprehensive coverage includes even remote areas, making it a go to for travelers and commuters.
    Whether you're navigating in unknown areas or exploring remote landmarks, Google Maps is +ure to provide accurate
    mapping data.\cite{GoogleMaps} \newline

    Google Maps began as a C++ desktop program developed by two Danish software engineers who so happens to be brothers,
    Lars Eilstrup Rasmussen and Jens Eilstrup Rasmussen.\cite{GoogleMaps} \newline

    \textbf{What is Apple Maps}

    Apple Maps is mostly the same as Google Maps, it also has very detailed mapping data.
    Apple Maps also provide a navigation function like Google Maps that is with turn-by-turn directions for driving,
    walking and public transportation.
    It also supports real-time traffic information and alternative routes to help users reach their destination more
    efficiently.
    Apple Maps can provide various information about shopping centers, restaurants, hotels and gas stations.
    Some of that information includes user reviews, photos, contact details and hours of operation.
    Google Maps does also provide this kind of information. \newline

    Google Maps used to be the default web mapping service for iOS, but they replaced Google Maps with their own version
    which is of course Apple Maps now. \cite{AppleMapsWiki} \newline

    \bibliography{simon}
    \bibliographystyle{unsrt}
\end{document}
